Initial Analysis

### 2019-05-25 Initial_Analysis.Rmd
Trying to figure out windows parallel

```{r Routine, eval = F, echo = F}

# Step 1; EstNeighbordList 
Neighbor_List <- EstNeighbors(Test)
# Neighbor_List <- EstNeighbors(World_EEZs)
# head(Neighbor_List)

# Step 2; EstTransIndex 
system.time(
  Spp_Trans <- bind_rows(
    lapply(
      Exploited_Species_List, FUN=EstTransIndex, EEZ_Size = EEZ_Size, Model = "All", Neighbors = Neighbor_List
    )
  )
)

>>>>

```{r Routine_parallel_Windows, eval = F, echo = F}

## Step 1: Create a cluster of child processes 
# Check number of cores
n_Cores <- detectCores()
n_Cores 
cl <- makeCluster(n_Cores)

## Step 2: Load the necessary R package(s)
## N.B. length(cl) is the number of child processes
##      in the cluster 
par.setup <- parLapply( cl, 1:length(cl),
    function(xx) {
        require(packages) 
    })

## Step 3: Distribute the necessary R objects 
clusterExport( cl, c('Neighbor_List') )

## Step 4: Do the computation
par.output <- parLapply(cl, 1:4,
    function(xx) {
       return( EstTransIndex(xx) + Neighbor_List )
    })

## Step 5: Remember to stop the cluster!
stopCluster(cl)
